Title

### 2024-06-11 paper/main.tex
Updates

\section{Measure of Association for mixed data}
In this section, we use canonical correlations to define an effect size measure
for mixed data CI tests. Our approach is similar to the approach used for the
continuous variable case.

@@

\subsection{Connection to special cases}
This natually is a generalization of partial correlations. Furthermore, it is 
also a generalization of discrete case.

>>>>

\section{A Measure of Association for Mixed Data}
In the previous section, we outlined measure of associations for different data
types, however we do not have any measure of association for a mixture of
categorical, ordinal, and continuous data. In this section, we develop a
measure of association for mixed data as a generalization of partial
correlation by combining a mixed data residualization approach with canonical
correlations.

\subsection{Mixed Data Residualization}

@@

\subsection{Connections to other measures}
This natually is a generalization of partial correlations. Furthermore, it is 
also a generalization of discrete case.
